HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-09-22 paper/main.tex
minor

%Could reinstate
After a brief review (\secref{sec:background}), we describe HUME in detail
(\secref{sec:hume}). 
Our experiments with four language pairs: English to Czech, German, Polish and Romanian (\secref{sec:experiments}) document HUME's inter-annotator agreement and efficiency (time of annotation). We further empirically compare HUME with direct assessment of human adequacy ratings, and conclude by discussing the differences with HMEANT (\secref{sec:hmeant_comp}).

@@

\paragraph{MT Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language
%\parcite{lopez2008statistical}.
Human evaluation is generally done by ranking the outputs of multiple systems
e.g., in the WMT tasks \parcite{bojar2015findings}, or by assigning
adequacy/fluency scores to each translation, a procedure recently improved
by \perscite{graham2015accurate} and called direct assessment. We use this method to compare and contrast
with HUME later in the paper. HTER~\parcite{snover2006study} is another widely used human evaluation metric
which uses edit distance metrics to compare a translation and its human 
post-edition. HTER suffers from the problem that small edits in the translation
could in fact be serious flaws in accuracy, eg. deleting a negation. 
Some manual measures ask annotators to explicitly mark errors, which however
suffers from even lower agreement than ranking \parcite{lommel:etal:mqm-iaa:2014}.

@@

In order to address this shortcoming, more recent work quantified
the similarity of the reference and translation in terms
of their structure. \perscite{liu2005syntactic} took a syntactic approach, 
using dependency grammar, and
\perscite{owczarzak2007evaluating} took a similar approach using lexical-functional grammar structures.
\perscite{gimenez2007linguistic} proposed to combine multiple types of information,
capturing the overlap between the translation and reference in terms of their
semantic (predicate-argument structures), lexical and morphosyntactic features.
\perscite{machacek:bojar:segranks:2015} divided the source sentences into shorter segments,
defined using a phrase structure parse, and applied human ranking to the resulting segments.

@@

\paragraph{Semantic Representation.}
UCCA (Universal Conceptual Cognitive Annotation, \inparcite{abend2013universal}) is a
cross-linguistically applicable scheme for semantic annotation.
Formally, an UCCA structure is a directed acyclic graph (DAG),
whose leaves correspond to the words of the text.
The graph's nodes, called {\sc units}, are either terminals or several elements jointly
viewed as a single entity according to some semantic or cognitive consideration. Edges bear
a category, indicating the role of the sub-unit in the structure the unit
represents.

UCCA's basic inventory of distinctions (its {\it foundational layer})
focuses on argument structures (adjectival, nominal, verbal and others)
and relations between them. The most basic notion is the Scene, which describes a movement, an
action or a state which persists in time. Each Scene contains one main
relation and zero or more participants. For example, the sentence ``After graduation, Tom moved to America''
contains two Scenes, whose main relations are ``graduation'' and ``moved''.
The participant ``Tom'' is a part of both Scenes, while ``America'' only of the
latter (\figref{fig:ucca_example_v2}). Further categories account for
inter-scene relations and the sub-structures of participants and relations.

% UCCA Motivation
The use of UCCA for semantic MT evaluation measure is motivated by two main reasons. 
First, UCCA's foundational layer can be annotated by non-experts after a short training
\parcite{abend2013universal,marinotti2014}.
Second, UCCA is cross-linguistically applicable, seeking to
represent what is shared between languages by building on
linguistic typological theory \parcite{Dixon:10a,Dixon:10b,Dixon:12}.
Its cross-linguistic applicability has so far been tested in annotations of
English, French, German and Czech.
Third, the scheme has been shown to be stable across translations:
UCCA annotations of translated text usually contain the same set of relations
\parcite{sulem2015conceptual}, indicating that UCCA reflects a layer of
representation that in a correct translation is mostly shared between
the translation and the source.

@@

The Abstract Meaning Representation (AMR) \parcite{banarescu2013abstract} project
shares UCCA's motivation for defining a more complete semantic annotation.
However, using AMR is not optimal for defining a decomposition of a sentence into semantic
units as it does not anchor its semantic symbols in the text,
and thus does not provide clear decomposition of the sentence into sub-units.
Also, AMR is more fine-grained than UCCA and consequently harder to annotate.
Other approaches represent semantic structures as bi-lexical dependencies
\parcite{sgallhp:1986,hajic2012announcing,oepen2006discriminant},
which are indeed anchored in the text, but are less suitable for MT evaluation
as they require linguistic expertise for their annotation.

@@

This section summarises the manual annotation procedure used
to compute the HUME measure. 
We denote the source sentence as $s$ and the translation as $t$. 
The procedure involves two manual steps: (1) UCCA-annotating $s$, 
(2) HUME-annotation: human judgements as to the translation quality of each semantic
unit of $s$ relative to $t$,
where units are defined according to the UCCA annotation.
UCCA annotation is performed once for every source sentence,
irrespective of the number of its translations we wish to evaluate,
and requires proficiency in the source language only.
HUME annotation requires the employment of bilingual annotators
\footnote{Where bilingual annotators are not available,
  the evaluation could be based on the UCCA structure for the
  \emph{reference} translation. See discussion in \secref{sec:hmeant_comp}.}

\paragraph{UCCA Annotation.}
We begin by creating UCCA annotations for the source sentence, following the
UCCA guidelines\footnote{All UCCA-related resources can be found
  here: \url{http://www.cs.huji.ac.il/~oabend/ucca.html}}.
A UCCA annotation for a sentence $s$ is a labeled DAG $G$, whose leaves
are the words of $s$.
For every node in $G$, we define its {\it yield} to be its leaf descendants.
The semantic units for $s$ according to $G$ are the yields of nodes in $G$.

@@

Annotation of the semantic units requires first deciding whether
a unit is {\it structural}, i.e., has meaning-bearing sub-units also in the
target language, or {\it atomic}.
In most cases, atomic units
correspond to individual words, but they may also correspond to
multi-word expressions that translate as one unit. For instance,
the expression ``took a shower'' is translated into the German ``duschte'',
while its individual words do not correspond to any sub-part of the German translation,
motivating the labeling the entire expression as an atomic node.
When a multi-word unit is labeled as atomic, its sub-units' annotations are ignored
in the evaluation.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.35\textwidth]{ucca-tree-mteval-v3.png}
    \end{center}
  \caption{\label{fig:hume_tree_v2}
     HUME annotation of an UCCA tree with a word aligned example translation shown below. 
     Atomic units are labelled using traffic lights (Red, Orange, Green) and structural
     units are marked A or B.}
\end{figure}
% Ondrej removes the following, he thinks that errors are not supposed to be
% propagated in HMEANT either:
%In HMEANT, it is not clear whether errors should be propegated up the SRL hierarchy.

Figure~\ref{fig:hume_tree_v2} presents an example of a HUME
annotation, where the translation is in English for ease of comprehension.
When evaluating ``to America'' the annotator looks at the translation and sees the
word ``stateside''. This word captures the whole phrase and so we mark this
non-leaf node with an atomic label. Here we choose Orange since
it approximately captures the meaning in this context.
The ability to mark non-leaves with atomic labels allows
the annotator to account for translations which only correspond at the phrase
level. Another feature highlighted in this example is that by separating structural
and atomic units, we are able to define where an error occurs, and localise
the error to its point of origin. The linker ``After'' is translated incorrectly as ``by''
which changes the meaning of the entire sentence. This error is captured at
the atomic level, and it is labelled Red. The sentence still contains two scenes and
a linker and therefore we mark the root node as structurally correct, Adequate.

@@

The interface presents, for each unit, the translation segment aligned with it.
This allows the user, especially in long sentences, to focus her attention on the parts
most likely to be relevant for her judgement. As the alignments are automatically derived,
and therefore noisy, the annotator is instructed to treat the aligned text is a cue, but to ignore
the alignment if it is misleading, and instead 
make a judgement according to the full translation.
Concretely, let $s$ be a source sentence, $t$ a translation,
and $A \subset 2^s \times 2^t$ a many-to-many word alignment.
If $u$ is a semantic unit in $s$, whose yield is $yld(u)$, we define the aligned text in
$t$ to be $\bigcup_{(x_s,x_t) \in A \wedge x_s \cap yld(u) \neq \emptyset} x_t$.

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \parcite{Koehn:2007}.  These were trained on large parallel data sets extracted from
OPUS \parcite{tiedemann:2009}, and the data sets released for the WMT14
medical translation task \parcite{bojar-EtAl:2014:W14-33}, 
giving between 45 and 85 million sentences of training data, depending on language pair.
%\oa{I think we should probably
%  say how many in each.}.
% ... if someone asks us to do so...
These translation systems were used to translate texts derived from both NHS
24\footnote{\url{http://www.nhs24.com/}} and
Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages.
NHS~24 is a public body providing healthcare and health-service
related information in Scotland; Cochrane is an international NGO
which provides independent systematic reviews on health-related research.
NHS~24 texts come from the ``Health A-Z'' section in the NHS Inform
website, and Cochrane texts come from their plain language summaries
and abstracts.

@@

The source sentences are all in English, and their UCCA annotation was performed by four
computational linguists and one linguist.
For the annotation of the MT output, we recruited two annotators for each of German, Romanian
and Polish and one main annotator for Czech. For Czech IAA,
several further annotators worked on a small number of 
sentences each. We treat these further annotators as one annotator, resulting in two annotators
for each language pair.
The annotators were all native speakers of the respective target languages and fluent in English.
They completed a three hour on-line training session where we described UCCA and the HUME task and then
we worked through a number of examples.

@@

\paragraph{Efficiency.}
We estimate the annotation time using the timestamps
provided by the annotation tool, which are recorded whenever an annotated sentence is
submitted. Annotators are not able to re-open a sentence once submitted. 
To estimate the annotation time, we compute the time difference between successive 
sentences, and discard outlying times since we assume annotation was not continuous.
From inspection of histograms of annotation times, we set the upper threshold at 500 seconds.
Median annotation times are presented in Table~\ref{tab:annot_times},
indicating that the annotation
of a sentence takes around 2--4 minutes, with some variation between annotators.

@@

In order to assess the consistency of the annotation, we measure the Inter-Annotator
Agreement (IAA) using Cohen's Kappa on the multiply-annotated units.
%For German, Polish and Romanian we used two annotators, with a significant overlap
%between the sentences they annotated. For Czech we had the entire batch
%annotated by one main annotator and multiple secondary annotators, 
%each annotating a sub-part of the batch.
\tabref{tab:iaa} reports the number of units which have two annotations from
different annotators and the corresponding Kappas.
%
%In order to compute Kappa, we consider the annotation task as a classification task on 
%nodes, and compute agreement on nodes which have two annotations from different annotators.
We report the overall Kappa, as well as separate Kappas on atomic
units (annotated as Red, Orange or Green) and structural units (annotated
as Adequate or Bad).
As expected and confirmed by confusion matrices in \figref{fig:heatmap}, there
is generally little confusion between the two types of units.
This results in the Kappa for all units being considerably higher than the kappa
over the atomic units or structural units, where there is more internal confusion.

@@

%presents the variance of kappa with length in each bin covers
%a length range of 10. and we show .

@@

To assess HUME reliability for long sentences,
we binned the sentences according to length and measured Kappa on each bin
(\figref{fig:iaalength}).
%The Kappas for each bin is presented in 
%\figref{fig:iaalength}.
%Results show that there is
We see
no discernible reduction of IAA with sentence
length. Also, from \tabref{tab:iaa} the overall IAA
is similar for all languages, showing good agreement (0.6--0.7).
However, there are differences observed when we break down by node type.
Specifically, we see a contrast  between
Czech and Polish, where the IAA is higher for atomic than for structural units, and German and Romanian,
where the reverse is true. We also observe low IAA (around 0.3) in the cases of
German atomic units, and Polish and Czech structural units.

@@

Looking more closely at the areas of disagreement, we see that for the Polish structural units, the 
proportion of As was quite different between the two annotators (53\% vs. 71\%), whereas for other
languages the annotators agree in the proportions. We believe that this was because one of the Polish
annotators did not fully understand the guidelines for structural units, and percolated
errors up the tree, creating more Bs. For German atomic and Czech structural units, where Kappa is also around 0.3, the proportion of such units being marked as ``correct'' is relatively 
high, meaning that the class distribution is more skewed, so the expected agreement used in the
Kappa calculation is high, lowering Kappa.
%ssentially, the annotation problem is harder when the classes are more skewed.
Finally we note some evidence of domain-specific disagreements, for instance
the German MT system normally translated ``review'' (as in ``systematic review'' -- a frequent term in the 
Cochrane texts) as ``\"uberpr\"ufung'', which 
one annotator marked correct, and the other (a Cochrane employee) as incorrect.

\subsection{Comparison with Direct Assessment}\label{sec:adequacy}

@@

Figure~\ref{fig:dacorrelation} plots the HUME score for each sentence against
its DA score. HUME and Direct Assessment scores correlate reasonably well. The
Pearson correlation for en-ro (en-de) is 0.70 (0.58), or 0.78 (0.74) if only
doubly HUME-annotated points are considered.
This confirms that HUME is consistent with an accepted human evaluation method,
despite the differences in their conception.
While DA is a valuable tool, HUME has two advantages:
it returns fine-grained semantic information about 
the quality of translations and it only requires very few annotators.
Direct assessment returns a single opaque score, and (as also noted by
Graham et al.) requires a large crowd which may not be available or reliable.

@@

Figure~\ref{fig:dacorrelationtypes} presents an analysis of HUME's correlations with DA by HUME unit type,
an analysis enabled by HUME's semantic decomposition. 
For both target languages, correlation is highest in the 'all' case, supporting our claim for the value of aggregating over a wide range of semantic phenomena. Some types of nodes predict the DA scores better than others. HUME scores on As correlate more strongly with DA than scores on Scene Main Relations (P+S). Center nodes (C) are also more correlated than elaborator nodes (E), which is expected given that Centers are defined to be more semantically dominant. Future work will construct an aggregate HUME score which weights the different node types according to their semantic relevance.

@@

While a quantitative comparison between DA and HUME, as we have just presented, is telling of their
differences and commonalities, it is important to note that the two measures are fundamentally different.
Figure~\ref{fig:humeeg} presents an example of a doubly HUME-annotated English-German example
accompanied by 10 raw DA scores assigned to that sentence. 
While DA standardises and averages scores across annotators to denoise the raw data, and obtain
a single aggregate score, HUME decomposes over a combinatorial structure, thus allowing
to localize the translation errors.
%Comparing DA and HUME is important in order to see where they agree and to
%determine under what circumstances it would be appropriate to apply each method.

@@

HMEANT focuses on verbal argument structures, ignoring other pervasive phenomena such as non-verbal predicates and inter-clause relations. Consider the following example:

@@

The German translation is largely correct, although the English verb ``tend''
was translated into the German prepositional phrase ``in der Regel'' (``as a rule'').
HMEANT will consider the translation to be of poor quality as there is no German verb
to align the English one with.

@@

We conducted an analysis of the English UCCA Wikipedia corpus (5324 sentences) in order to assess the
pervasiveness of three phenomena that are not well supported by HMEANT.\footnote{Argument structures and
linkers are explicitly marked in UCCA. Non-auxiliary instances of ``be'' and nouns are identified using
the NLTK standard tagger. Nominal argument structures are here Scenes whose main relation is headed by a noun.}
First, copula clauses are treated in HMEANT simply as instances of the main verb ``be'', which generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences, according to conservative estimates that only consider non-auxiliary instances of ``be''. Second, nominal argument structures, ignored by HMEANT, are in fact highly pervasive, appearing in 48.7\% of the sentences. Third, linkers that express inter-relations between clauses (mainly discourse markers and conjunctions) appear in 56\% of the sentences, but are again ignored by HMEANT. For instance, linkers are sometimes omitted in translation, but these omissions are not penalized by HMEANT. The following is such an example from our experimental dataset:

@@

All annotation data gathered in this project, together with analysis scripts is available
online\footnote{\url{https://github.com/bhaddow/hume-emnlp16}}.

@@

%As you can see 
As can be seen
in Figure~\ref{ucca-tree}, the UCCA annotation results in a tree structure where each leaf is linked to
a word in the sentence at the bottom. A scene must contain a process (P) or a state (S). It can also contain
participants (A) and it can be linked to other scenes by a linker (Linker). Participants, processes and states can be
further analysed into elaborators (E), centres (C) and relators (R). These labels are very 
%high level 
high-level 
and relate to
cognitive concepts which should remain stable across languages.

@@

UCCA provides universal semantic structures which 
%has 
have
a minimal set of labels. It provides a complete semantic tree which does not rely on syntactic heads and the semantic structure is grounded directly to the words in the sentence. 
 Even though the set of UCCA labels are fairly restricted,  nevertheless they allow us to determine the most important components of the graph (for example it defines centres and linkers which would be likely to carry more weight than elaborators), and we can use this to better calculate the score. 
We think that UCCA is the
most promising representation for evaluating translation. 
}

>>>>

%Could reinstate
After a brief review (\secref{sec:background}), we describe HUME in detail
(\secref{sec:hume}). 
Our experiments with four language pairs: English to Czech, German, Polish and Romanian (\secref{sec:experiments}) document HUME's inter-annotator agreement and efficiency (time of annotation). We further empirically compare HUME with direct assessment of human adequacy ratings (\secref{sec:adequacy}), and conclude by discussing the differences with HMEANT (\secref{sec:hmeant_comp}).

@@

\paragraph{MT Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language
%\parcite{lopez2008statistical}.
Human evaluation is generally done by ranking the outputs of multiple systems
e.g., in the WMT tasks \parcite{bojar2015findings}, or by assigning
adequacy/fluency scores to each translation, a procedure recently improved
by \perscite{graham2015accurate} under the title Direct Assessment. We use this method to compare and contrast
with HUME later in the paper. HTER~\parcite{snover2006study} is another widely used human evaluation metric
which uses edit distance metrics to compare a translation and its human 
post-edition. HTER suffers from the problem that small edits in the translation
could in fact be serious flaws in accuracy, e.g., deleting a negation. 
Some manual measures ask annotators to explicitly mark errors, but this has
been found to have even lower agreement than ranking \parcite{lommel:etal:mqm-iaa:2014}.

@@

In order to address this shortcoming, more recent work quantified
the similarity of the reference and translation in terms
of their structure. \perscite{liu2005syntactic} took a syntactic approach, 
using dependency grammar, and
\perscite{owczarzak2007evaluating} took a similar approach using Lexical Functional Grammar structures.
\perscite{gimenez2007linguistic} proposed to combine multiple types of information,
capturing the overlap between the translation and reference in terms of their
semantic (predicate-argument structures), lexical and morphosyntactic features.
\perscite{machacek:bojar:segranks:2015} divided the source sentences into shorter segments,
defined using a phrase structure parse, and applied human ranking to the resulting segments.

@@

\paragraph{Semantic Representation.}
UCCA (Universal Conceptual Cognitive Annotation) \cite{abend2013universal} is a
cross-linguistically applicable scheme for semantic annotation.
Formally, an UCCA structure is a directed acyclic graph (DAG),
whose leaves correspond to the words of the text.
The graph's nodes, called {\it units}, are either terminals or several elements jointly
viewed as a single entity according to some semantic or cognitive consideration. Edges bear
a category, indicating the role of the sub-unit in the structure the unit
represents.

UCCA's basic inventory of distinctions (its {\it foundational layer})
focuses on argument structures (adjectival, nominal, verbal and others)
and relations between them. The most basic notion is the {\it Scene}, which describes a movement, an
action or a state which persists in time. Each Scene contains one main
relation and zero or more participants. For example, the sentence ``After graduation, Tom moved to America''
contains two Scenes, whose main relations are ``graduation'' and ``moved''.
The participant ``Tom'' is a part of both Scenes, while ``America'' only of the
latter (\figref{fig:ucca_example_v2}). Further categories account for
inter-scene relations and the sub-structures of participants and relations.

% UCCA Motivation
The use of UCCA for semantic MT evaluation has several motivations. 
First, UCCA's foundational layer can be annotated by non-experts after a short training
\parcite{abend2013universal,marinotti2014}.
Second, UCCA is cross-linguistically applicable, seeking to
represent what is shared between languages by building on
linguistic typological theory \parcite{Dixon:10a,Dixon:10b,Dixon:12}.
Its cross-linguistic applicability has so far been tested in annotations of
English, French, German and Czech.
Third, the scheme has been shown to be stable across translations:
UCCA annotations of translated text usually contain the same set of relations
\parcite{sulem2015conceptual}, indicating that UCCA reflects a layer of
representation that in a correct translation is mostly shared between
the translation and the source.

@@

The Abstract Meaning Representation (AMR) \parcite{banarescu2013abstract}
shares UCCA's motivation for defining a more complete semantic annotation.
However, using AMR is not optimal for defining a decomposition of a sentence into semantic
units as it does not anchor its semantic symbols in the text,
and thus does not provide clear decomposition of the sentence into sub-spans.
Also, AMR is more fine-grained than UCCA and consequently harder to annotate.
Other approaches represent semantic structures as bi-lexical dependencies
\parcite{sgallhp:1986,hajic2012announcing,oepen2006discriminant},
which are indeed anchored in the text, but are less suitable for MT evaluation
as they require linguistic expertise for their annotation.

@@

This section summarises the manual annotation procedure used
to compute the HUME measure. 
We denote the source sentence as $s$ and the translation as $t$. 
The procedure involves two manual steps: (1) UCCA-annotating $s$, 
(2) HUME-annotation: human judgements as to the translation quality of each semantic
unit of $s$ relative to $t$,
where units are defined according to the UCCA annotation.
UCCA annotation is performed once for every source sentence,
irrespective of the number of its translations we wish to evaluate,
and requires proficiency in the source language only.
HUME annotation requires the employment of bilingual
annotators.\footnote{Where bilingual annotators are not available,
  the evaluation could be based on the UCCA structure for the
  \emph{reference} translation. See discussion in \secref{sec:hmeant_comp}.}

\paragraph{UCCA Annotation.}
We begin by creating UCCA annotations for the source sentence, following the
UCCA guidelines.\footnote{All UCCA-related resources can be found
  here: \url{http://www.cs.huji.ac.il/~oabend/ucca.html}}
A UCCA annotation for a sentence $s$ is a labeled DAG $G$, whose leaves
are the words of $s$.
For every node in $G$, we define its {\it yield} to be its leaf descendants.
The semantic units for $s$ according to $G$ are the yields of nodes in $G$.

@@

Annotation of the semantic units requires first deciding whether
a unit is {\it structural}, i.e., has meaning-bearing
sub-units in the target language, or {\it atomic}.
In most cases, atomic units
correspond to individual words, but they may also correspond to
multi-word expressions that translate as one unit. For instance,
the expression ``took a shower'' is translated into the German ``duschte'',
while its individual words do not correspond to any sub-part of the German translation,
motivating the labeling the entire expression as an atomic node.
When a multi-word unit is labeled as atomic, its sub-units' annotations are ignored
in the evaluation.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.35\textwidth]{ucca-tree-mteval-v3.png}
    \end{center}
  \caption{\label{fig:hume_tree_v2}
     HUME annotation of an UCCA tree with a word-aligned example translation shown below. 
     Atomic units are labelled using traffic lights (Red, Orange, Green) and structural
     units are marked A or B.}
\end{figure}
% Ondrej removes the following, he thinks that errors are not supposed to be
% propagated in HMEANT either:
%In HMEANT, it is not clear whether errors should be propegated up the SRL hierarchy.

Figure~\ref{fig:hume_tree_v2} presents an example of a HUME
annotation, where the translation is in English for ease of comprehension.
When evaluating ``to America'' the annotator looks at the translation and sees the
word ``stateside''. This word captures the whole phrase and so we mark this
non-leaf node with an atomic label. Here we choose Orange since
it approximately captures the meaning in this context.
The ability to mark non-leaves with atomic labels allows
the annotator to account for translations which only correspond at the phrase
level. Another feature highlighted in this example is that by separating structural
and atomic units, we are able to define where an error occurs, and localise
the error to its point of origin. The linker ``After'' is translated incorrectly as ``by''
which changes the meaning of the entire sentence. This error is captured at
the atomic level, and it is labelled Red. The sentence still contains two Scenes and
a Linker and therefore we mark the root node as structurally correct, Adequate.

@@

The interface presents, for each unit, the translation segment aligned with it.
This allows the user, especially in long sentences, to focus her attention on the parts
that are most likely to be relevant for her judgement. As the alignments are automatically derived,
and therefore noisy, the annotator is instructed to treat the aligned text is a cue, but to ignore
the alignment if it is misleading, and instead 
make a judgement according to the full translation.
Concretely, let $s$ be a source sentence, $t$ a translation,
and $A \subset 2^s \times 2^t$ a many-to-many word alignment.
If $u$ is a semantic unit in $s$, whose yield is $yld(u)$, we define the aligned text in
$t$ to be $\bigcup_{(x_s,x_t) \in A \wedge x_s \cap yld(u) \neq \emptyset} x_t$.

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \parcite{Koehn:2007}.  These were trained on large parallel data sets extracted from
OPUS \parcite{tiedemann:2009}, and the data sets released for the WMT14
medical translation task \parcite{bojar-EtAl:2014:W14-33}, 
giving between 45 and 85 million sentences of training data, depending on the language pair.
%\oa{I think we should probably
%  say how many in each.}.
% ... if someone asks us to do so...
These translation systems were used to translate texts derived from both NHS
24\footnote{\url{http://www.nhs24.com/}} and
Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages.
NHS~24 is a public body providing healthcare and health-service
related information in Scotland; Cochrane is an international NGO
which provides independent systematic reviews on health-related research.
NHS~24 texts come from the ``Health A-Z'' section in the NHS Inform
website, and Cochrane texts come from their plain language summaries
and abstracts.

@@

The source sentences are all in English, and their UCCA annotation was performed by four
computational linguists and one linguist.
For the annotation of the MT output, we recruited two annotators for each of German, Romanian
and Polish and one main annotator for Czech. For computing Czech IAA,
several further annotators worked on a small number of 
sentences each. We treat these further annotators as one annotator, resulting in two annotators
for each language pair.
The annotators were all native speakers of the respective target languages and fluent in English.
They completed a three hour on-line training session which included a description of
UCCA and the HUME task, followed by walking through a few examples.

@@

\paragraph{Efficiency.}
We estimate the annotation time using the timestamps
provided by the annotation tool, which are recorded whenever an annotated sentence is
submitted. Annotators are not able to re-open a sentence once submitted. 
To estimate the annotation time, we compute the time difference between successive 
sentences, and discard outlying times, assuming annotation was not continuous in these cases.
From inspection of histograms of annotation times, we set the upper threshold at 500 seconds.
Median annotation times are presented in Table~\ref{tab:annot_times},
indicating that the annotation
of a sentence takes around 2--4 minutes, with some variation between annotators.

@@

In order to assess the consistency of the annotation, we measure the Inter-Annotator
Agreement (IAA) using Cohen's Kappa on the multiply-annotated units.
%For German, Polish and Romanian we used two annotators, with a significant overlap
%between the sentences they annotated. For Czech we had the entire batch
%annotated by one main annotator and multiple secondary annotators, 
%each annotating a sub-part of the batch.
\tabref{tab:iaa} reports the number of units which have two annotations from
different annotators and the corresponding Kappas.
%
%In order to compute Kappa, we consider the annotation task as a classification task on 
%nodes, and compute agreement on nodes which have two annotations from different annotators.
We report the overall Kappa, as well as separate Kappas on atomic
units (annotated as Red, Orange or Green) and structural units (annotated
as Adequate or Bad).
As expected and confirmed by confusion matrices in \figref{fig:heatmap}, there
is generally little confusion between the two types of units.
This results in the Kappa for all units being considerably higher than the Kappa
over the atomic units or structural units, where there is more internal confusion.

@@

%presents the variance of Kappa with length in each bin covers
%a length range of 10. and we show .

@@

To assess HUME reliability for long sentences,
we binned the sentences according to length and measured Kappa on each bin
(\figref{fig:iaalength}).
%The Kappas for each bin is presented in 
%\figref{fig:iaalength}.
%Results show that there is
We see
no discernible reduction of IAA with sentence
length. \tabref{tab:iaa} also shows that the overall IAA
is similar for all languages, presenting good agreement (0.6--0.7).
However, there are differences observed when we break down by node type.
Specifically, we see a contrast  between
Czech and Polish, where the IAA is higher for atomic than for structural units, and German and Romanian,
where the reverse is true. We also observe low IAA (around 0.3) in the cases of
German atomic units, and Polish and Czech structural units.

@@

Looking more closely at the areas of disagreement, we see that for the Polish structural units, the 
proportion of As was quite different between the two annotators (53\% vs. 71\%), whereas for other
languages the annotators agree in the proportions. We believe that this was because one of the Polish
annotators did not fully understand the guidelines for structural units, and percolated
errors up the tree, creating more Bs. For German atomic and Czech structural units, where Kappa is also around 0.3, the proportion of such units being marked as ``correct'' is relatively 
high, meaning that the class distribution is more skewed, so the expected agreement used in the
Kappa calculation is high, lowering Kappa.
%ssentially, the annotation problem is harder when the classes are more skewed.
Finally we note some evidence of domain-specific disagreements, for instance
the German MT system normally translated ``review'' (as in ``systematic review'' -- a frequent term in the 
Cochrane texts) as ``\"Uberpr\"ufung'', which 
one annotator marked correct, and the other (a Cochrane employee) as incorrect.

\section{Comparison with Direct Assessment}\label{sec:adequacy}

@@

Figure~\ref{fig:dacorrelation} plots the HUME score for each sentence against
its DA score. HUME and Direct Assessment scores correlate reasonably well. The
Pearson correlation for en-ro (en-de) is 0.70 (0.58), or 0.78 (0.74) if only
doubly HUME-annotated points are considered.
This confirms that HUME is consistent with an accepted human evaluation method,
despite their conceptual differences.
While DA is a valuable tool, HUME has two advantages:
it returns fine-grained semantic information about 
the quality of translations and it only requires very few annotators.
Direct assessment returns a single opaque score, and (as also noted by
Graham et al.) requires a large crowd which may not be available or reliable.

@@

Figure~\ref{fig:dacorrelationtypes} presents an analysis of HUME's correlations with DA by HUME unit type,
an analysis enabled by HUME's semantic decomposition. 
For both target languages, correlation is highest in the 'all' case, supporting our claim for the value of aggregating over a wide range of semantic phenomena. Some types of nodes predict the DA scores better than others. HUME scores on As correlate more strongly with DA than scores on Scene Main Relations (P+S). Center nodes (C) are also more correlated than elaborator nodes (E), which is expected given that Centers are defined to be more semantically dominant. Future work will construct an aggregate HUME score which weights the different node types according to their semantic prominence.

@@

%While a quantitative comparison between DA and HUME, as we have just presented, is telling of their
%differences and commonalities, it is important to note that the two measures are fundamentally different.
Figure~\ref{fig:humeeg} presents an example of a doubly HUME-annotated English-German example
accompanied by 10 raw DA scores assigned to that sentence.
The figure illustrates the conceptual difference between the measures:
while DA standardises and averages scores across annotators to denoise the
crowd-sourced raw data, thus obtaining a single aggregate score,
HUME decomposes over a combinatorial structure, thus allowing to
localize the translation errors. We turn to comparing HUME to a more
conceptually-related  measure, namely HMEANT.

%Comparing DA and HUME is important in order to see where they agree and to
%determine under what circumstances it would be appropriate to apply each method.

@@

HMEANT focuses on verbal argument structures, ignoring other pervasive phenomena such as non-verbal predicates and inter-clausal relations. Consider the following example:

@@

The German translation is largely correct, despite the grammatical divergence,
namely that the English verb ``tend''
is translated into the German prepositional phrase ``in der Regel'' (``as a rule'').
HMEANT will consider the translation to be of poor quality as there is no German verb
to align with the English one.

@@

We conducted an analysis of the English UCCA Wikipedia corpus (5324 sentences) in order to assess the
pervasiveness of three phenomena that are not well supported by HMEANT.\footnote{Argument structures and
linkers are explicitly marked in UCCA. Non-auxiliary instances of ``be'' and nouns are identified using
the NLTK standard tagger. Nominal argument structures are here Scenes whose Main Relation is headed by a noun.}
First, copula clauses are treated in HMEANT simply as instances of the main verb ``be'', which generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences, according to conservative estimates that only consider non-auxiliary instances of ``be''. Second, nominal argument structures, ignored by HMEANT, are in fact highly pervasive, appearing in 48.7\% of the sentences. Third, linkers that express inter-relations between clauses (mainly discourse markers and conjunctions) appear in 56\% of the sentences, but are again ignored by HMEANT. For instance, linkers are sometimes omitted in translation, but these omissions are not penalized by HMEANT. The following is such an example from our experimental dataset:

@@

All annotation data gathered in this project, together with analysis scripts, is available
online\footnote{\url{https://github.com/bhaddow/hume-emnlp16}}.

@@

%As you can see 
As can be seen
in Figure~\ref{ucca-tree}, the UCCA annotation results in a tree structure where each leaf is linked to
a word in the sentence at the bottom. A scene must contain a process (P) or a state (S). It can also contain
participants (A) and it can be linked to other scenes by a Linker (Linker). Participants, processes and states can be
further analysed into elaborators (E), centres (C) and relators (R). These labels are very 
%high level 
high-level 
and relate to
cognitive concepts which should remain stable across languages.

@@

UCCA provides universal semantic structures which 
%has 
have
a minimal set of labels. It provides a complete semantic tree which does not rely on syntactic heads and the semantic structure is grounded directly to the words in the sentence. 
 Even though the set of UCCA labels are fairly restricted,  nevertheless they allow us to determine the most important components of the graph (for example it defines centres and Linkers which would be likely to carry more weight than elaborators), and we can use this to better calculate the score. 
We think that UCCA is the
most promising representation for evaluating translation. 
}
